\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex
Added RMSE comparisons

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/6-Way-Comparison-Feat-Density-1215-1715-Trans}
        \label{fig:comp_3:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/6-Way-Comparison-Feat-Density-1215-1715-Rot}
        \label{fig:comp_3:rot_err}
    }

>>>>

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Trans}
        \label{fig:comp_3:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Rot}
        \label{fig:comp_3:rot_err}
    }
